\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sagar Chaudhari} % Your name
% You can merge both of these into a single line, if you do not have a website. 
\address{\href{mailto:sbchaudhari581@gmail.com}{sbchaudhari581@gmail.com} \\ \href{https://www.linkedin.com/in/sagar-chaudhari-588864208}{LinkedIn} \\ 
\href{https://github.com/sagar581}{Github} \\ 
\href{tel:962-450-4823}{+91 9624504823}}  %

\begin{document}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Dhirubhai Ambani Institute of Information \& Communication Technology, Gujarat } \hfill {\textbf{2019 - 2023}}

B.Tech in Information and Communication Technology\hfill \textit{\textbf{CGPA : 7.07}}
%{\bf AISSCE (Class XII)}, Delhi Public School, Bokaro, India \hfill {2016 - 2018} \\
%Aggregate: 90.5\%

\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills &  Android SDK, XML, Compose, Hilt, KMM, REST APIs, SQL, WebView, \\ & MVVM, Firebase, Coroutines, Git, Bitbucket, Bitrise CI/CD
\\
Area(s) of Interest & Android, Backend, Problem Solving, OOPs, Debugging, DSA, AI/ML
\\
Programming Languages & Kotlin, Python, C\#, C++, JavaScript\\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------


\begin{rSection}{EXPERIENCE}

\textbf{SSDE - Android } \hfill \textbf{Sept 2024 - Present}\\
\textbf{\href{https://www.linkedin.com/company/freecharge-in/}{Dhani Stocks Limited}}   \hfill \textit{Gurugram, India}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Acquired comprehensive knowledge of \textbf{fintech} systems and evaluated tech stacks like \textbf{Flutter and KMM} for app redesign, demonstrating a \textbf{strong ability} to assess technologies and align them with \textbf{business goals}.
    
    \item Integrated Setu RPD, HDFC payment gateway in \textbf{WebView}, and Razorpay SDK into \textbf{Dhani Stocks} to deliver \textbf{reliable}, user-focused fintech solutions. Improved \textbf{problem-solving} skills by resolving multiple bugs, including critical inverted QR code scanning in \textbf{Dhani UPI}.
    
    \item Improved app \textbf{launch time and responsiveness}, strengthened skills in \textbf{debugging} and code reviews, and fostered teamwork to deliver high-quality, \textbf{scalable solutions} that are valuable for addressing complex \textbf{technical challenges} in any domain.
 \end{itemize}

\textbf{Software Development Engineer - Android } \hfill \textbf{July 2023 - July 2024}\\
\textbf{\href{https://www.linkedin.com/company/freecharge-in/}{Freecharge - DBAT by Axis Bank}}   \hfill \textit{Mumbai -- Remote}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Worked on \textbf{SubZero 2.0} for Android using \textbf{Kotlin/XML} and Collabrated with team and extended it to \textbf{iOS} with \textbf{Kotlin Multiplatform Mobile} and \textbf{Jetpack Compose} for future use. Improved \textbf{efficiency} and \textbf{user experience} for \textbf{Axis Bank apps.}
    
    \item Designed comprehensive \textbf{test suites} for SubZero 2.0 on \textbf{Android} and \textbf{iOS}, ensuring \textbf{high performance} and \textbf{reliability}. Reduced issues after release, boosting \textbf{client satisfaction.}

 \end{itemize}

\textbf{Software Developer - Intern } \hfill \textbf{Jan 2023 - May 2023}\\ 
\textbf{\href{https://www.linkedin.com/company/Clomotech/}{Clomotech Private Limited}} \hfill \textit{BTP Internship - Remote}
 \begin{itemize}
    \itemsep -3pt {} 
    
     \item Collaborated with \textbf{Monocept} and \textbf{ICICI Lombard} teams to migrate \textbf{Python} code to \textbf{C\#}, optimizing \textbf{efficiency} and \textbf{compatibility} across platforms.
     \item Developed and deployed an \textbf{AWS Lambda} function in C\#, based on existing Python code. Achieved a significant \textbf{54.34\% performance improvement} during load testing with \textbf{JMeter}, enhancing \textbf{scalability} and responsiveness for concurrent invocations.
     \item Developed a \textbf{user authentication} demo in C\# using \textbf{AWS Cognito}, implementing sign-up/sign-in functionality and \textbf{JWT token} generation in a team of two, \textbf{enhancing system security} by ensuring \textbf{robust} and \textbf{scalable} user authentication.

 \end{itemize}
 

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{WeatherApp.} {Developed a comprehensive Weather Forecast app using Android Studio, Retrofit, FCM, and the Gson library to provide real-time weather updates.}
\item \textbf{ToDo-List App.} {created a To-do List app with user authentication, utilizing the ROOM database for efficient data management and shared preferences for secure user login.}
\end{rSection} 



%----------------------------------------------------------------------------------------
\begin{rSection}{Achievements} 
\begin{itemize}
    \item   \textbf{296} ACPC rank in 12th Gujarat Board
    \item   ranked \textbf{24} in CodeChef Starters 36 contest
    \item   ranked \textbf{99} in CodeCheaf May Long One 2022
contest
    \item   \textbf{4-Star} on CodeChef (\textbf{Max:1927}):
    \href{https://www.codechef.com/users/checking}{\textbf{CodeChef}} 
\end{itemize}


\end{rSection}

\end{document}